MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-04-14 Manuscript/Manuscript-1-DCA.tex
paper vsn 1-DCA

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\usepackage{setspace}\doublespacing
\usepackage{lineno}\linenumbers
% https://github.com/rstudio/rmarkdown/issues/337
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

% https://github.com/rstudio/rmarkdown/pull/252
\usepackage{titling}
\setlength{\droptitle}{-2em}

\pretitle{\vspace{\droptitle}\centering\huge}
\posttitle{\par}

\preauthor{\centering\large\emph}
\postauthor{\par}

\predate{\centering\large\emph}
\postdate{\par}

\date{}

@@

\section{Pagel's Lambda Estimates are Often
Inaccurate}\label{pagels-lambda-estimates-are-often-inaccurate}

@@

\section{Abstract}\label{abstract}

@@

\section{Introduction}\label{introduction}

Investigating macroevolutionary patterns requires a phylogenetic
approach as species are non-independent by nature of their shared
ancestry. Since the first appropriate method was introduced by
Felsenstein (phylogenetic independent contrasts; Felsenstein (1985)),
dozens of other methods have been developed and applied to increasingly
complex questions in macroevolutionary biology (e.g. Grafen (1989);
Harvey and Pagel (1991); Rohlf (2001); ({\textbf{???}})). A particularly
useful measure in this field is phylogenetic signal, a quantification of
a trait's correspondence with the clade's phylogenic history.
Understanding the degree of phylogenetic signal present in a dataset is
paramount and identifies the mode under which a trait has evolved; high
measures of phylogenetic signal indicate a Brownian motion process,
whereas lower levels of phylogenetic signal indicate natural selection
or some other evolutionary force has influenced the traits evolutionary
history. \hfill\break

Several approaches to quantify phylogenetic signal exist. For continuous
data, the most common parameters used in the literature include Pagel's
lambda ({\textbf{???}}) and Blomberg's kappa ({\textbf{???}}). Pagel's
lambda has the advantage of being nested in the likelihood framework and
thus has also been utilized to simultaneously estimate and account for
phylogenetic signal while doing phylogenetic regressions or ANOVAs. At
the development of these estimation methods, clear recommendations on
the use and interpretation of this parameter were made based on data
simulations and error evaluations (Revell 2010). However, the accuracy
of the lambda estiamtion methods have not been fully evaluated, and
consequently many studies have substantially misused these methods.
\hfill\break

An earlier study ({\textbf{???}}), breifly addressed this topic by
showing how uninformative smaller phylogenies are when estimating
various evolutionary parameters, such as Pagel's lambda. However, it
remains unknown the degree to which lambda estimates accurately
represent degree of phylogenetic signal, and thus we fully explicate the
extent to which Pagel's lambda estimation methods can and have been
misused in recent macroevolutionary studies. Here we take a
comprehensive approach to demonstrate the scenarios under which
estimated Pagel's lambdas accurately reflect known lambdas. We then
demonstrate the effect of these, at times, dubious estimation methods on
significance testing when used in a PGLS framework. Finally, we perform
a meta-analysis of research published in 2019 employing Pagel's lambda
estimation methods to demonstrate the uses and misuses of this method in
the literature. This investigation provides evidence for the
circumstances under which estimating Pagel's lambda can be informative,
and which interpretations or uses are misleading with the hope of moving
the field towards more appropriate employment of phylogenetic
comparative methods.

\section{Methods and Results}\label{methods-and-results}

\subsection{\texorpdfstring{\emph{Simulated
trait}}{Simulated trait}}\label{simulated-trait}

@@

\subsection{\texorpdfstring{\emph{Simulated ANOVA and
Regressions}}{Simulated ANOVA and Regressions}}\label{simulated-anova-and-regressions}

@@

Scaling and trait generation procedures for all simulation methods were
repeated with symmetrical and ladder phylogenies of variable size.
Results generated using these variable phylogeny shapes were consistent
with the pure-birth phylogeny results presented above and can be found
in the Supplemental Materials. All analyses were performed in R v3.6.0
({\textbf{???}}) using the packages \texttt{geiger} ({\textbf{???}}) and
\texttt{caper} ({\textbf{???}}), and the corresponding scripts can be
found in the Supplemental Materials.

\subsection{\texorpdfstring{\emph{Meta-Analysis of Empirical
Results}}{Meta-Analysis of Empirical Results}}\label{meta-analysis-of-empirical-results}

To understand the extent of this problematic estimation method in
application, we performed a meta-analysis of studies published in 2019
that cited Pagel's 1997 manuscript ({\textbf{???}}). The list of
manuscripts was compiled through Google Scholar on Jan 23, 2020 and
totaled 341 manuscripts. For each study, we extracted any published
lambda estimates, along with the size of the phylogeny used in the
analysis. We also noted whether authors reported confidence intervals,
significance tests assessing difference of the lambda estimate from 0 or
1, and whether authors interpreted biological meaning from the magnitude
of the estimated lambda. For studies that reported more than one lambda
estimate, we also noted if the authors compared the lambdas against one
another, and whether that was accompanied with an appropriate
statistical test between the estimated lambda values. \hfill\break

@@

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

@@

\hypertarget{refs}{}
\hypertarget{ref-Felsenstein1985}{}
Felsenstein, J. 1985. Phylogenies and the comparative method. American
Naturalist 125:1--15.

\hypertarget{ref-Grafen1989}{}
Grafen, A. 1989. The phylogenetic regression. Philosophical Transactions
of the Royal Society of London B, Biological Sciences 326:119--157.

\hypertarget{ref-HarveyPagel1991}{}
Harvey, P. H., and M. D. Pagel. 1991. The comparative method in
evolutionary biology. Oxford University Press, Oxford.

\hypertarget{ref-Revell2010}{}
Revell, L. J. 2010. Phylogenetic signal and linear regression on species
data. Methods in Ecology and Evolution 1:319--329.

\hypertarget{ref-Rohlf2001}{}
Rohlf, F. J. 2001. Comparative methods for the analysis of continuous
variables: Geometric interpretations. Evolution 55:2143--2160.

@@

\section{Figure Legends}\label{figure-legends}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{setspace}\doublespacing
\usepackage{lineno}\linenumbers

\author{}
\date{\vspace{-2.5em}}

@@

\hypertarget{estimates-of-phylogenetic-signal-based-on-lambda-are-often-inaccurate}{%
\section{Estimates of Phylogenetic Signal Based on Lambda are Often
Inaccurate}\label{estimates-of-phylogenetic-signal-based-on-lambda-are-often-inaccurate}}

@@

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Investigating macroevolutionary patterns of trait variation requires a
phylogenetic perspective, because the shared ancestry among species
generates statistical non-independence (Felsenstein 1985; Harvey and
Pagel 1991). Accounting for this evolutionary non-independence is the
purview of \emph{phylogenetic comparative methods} (PCMs); a suite of
analytical tools that condition the data on the phylogeny through the
course of statisical evaluations of phenotypic trends (e.g., Grafen
1989; Garland and Ives 2000; Rohlf 2001; Butler and King 2004). The past
several decades have witnessed a rapid expansion in the development of
PCMs to address an ever-growing set of macroevolutionary hypotheses
(Martins and Hansen 1997; O'Meara et al. 2006; Revell and Harmon 2008;
Beaulieu et al. 2012; Adams 2014b,a; Adams and Collyer 2018). These
methods are predicated on the notion that phylogenetic signal -- the
tendancy for closely related species to display similar trait values --
is present in cross-species datasets (Abouheif 1999; Pagel 1999;
Blomberg et al. 2003; Munkemuller et al. 2012). Indeed, under numerous
evolutionary models, phylogenetic signal is to be expected, as
stochastic character change along the hierarchical structure of the tree
of life generates trait covaration among related taxa (see Felsenstein
1985; Blomberg et al. 2003; Revell et al. 2008). \hfill\break

In many macroevolutionary studies, it is often of interest to quantify
the degree to which phylogenetic signal is displayed in continuous
traits. Several analytical tools have been developed for this purpose
(e.g., Gittleman and Kot 1990; Abouheif 1999; Pagel 1999; Blomberg et
al. 2003; Klingenberg and Gidaszewski 2010; Adams 2014a), which differ
primarily in how they characterize the phylogenetic dependency of trait
variation among taxa. One commonly used statistical measure,
\emph{Kappa} (\(K\)), expresses the strength of phylogenetic signal as
the ratio of observed trait variation to the trait variation conditioned
on the phylogeny; scaled by what is expected under Brownian motion given
the phylogeny's size and shape (Blomberg et al. 2003; also Adams 2014a).
Another approach, Pagel's \(\lambda\) (Pagel 1999), uses maximum
likelihood to fit the data to the phylogeny under some model of
evolutionary change (typically Brownian motion). The inclusion of a
scaling parameter, \(\lambda\), transforms the lengths of the internal
branches of the phylogeny to improve the fit, and this parameter
describes the degree of phylogenetic signal in the dataset (Pagel 1999;
Freckleton et al. 2002). Pagel's \(\lambda\) also has the advantage that
it may be included when estimating the association of traits in a
phylogenetic context, meaning that one may account for the degree of
phylogenetic signal while conducting phylogenetic regression or ANOVA
(see Freckleton et al. 2002). \hfill\break

Several studies have investigated the statistical properties of methods
for estimating phylogenetic signal under various conditions (e.g.,
Munkemuller et al. 2012; Pavoine and Ricotta 2012; Diniz-Filho et al.
2012; Molina-Venegas and Rodriguez 2017; see also Revell et al. 2008;
Revell 2010). These have largely focused on the ability of methods to
detect the presence of phylogenetic signal (i.e., type I and type II
error rates) under complex models of evolutionary change, across a range
of phylogeny sizes, and with varying degrees of phylogenetic uncertainty
or unresolved topologies. In terms of parameter estimation, Revell
(2010) confirmed that regression parameters were accurately estimated
when \(\lambda\) was included during phylogenetic regression, and
Munkmuller et al.~(2012) found that estimates of phylogenetic signal
obtained using various measures generally increased when input levels of
phylogenetic signal were stronger. However, the precision of those
estimates could not be determined, because the input levels of
phylogenetic signal were simulated via a scaling factor (\(w\)) that was
not directly comparable to the measures of phylogenetic signal being
compared (see Munkemuller et al. 2012). One study (Boettiger et al.
2012) found that estimates of Pagel's \(\lambda\) displayed less
variation when data were simulated on a large phylogeny (\(N=281\)) as
compared to a small one (\(N=13\)), concluding that insufficient data
(i.e., the number of species) was the underlying cause of the lack of
precision in parameter estimation. However, this conclusion assumes that
parameter estimation remains equally precise across its range of values
(\(\lambda = 0 \to 1\)); an assumption that to date, has not been
investigated. Thus, despite widespread use of Pagel's (1999) \(\lambda\)
in macroevolutionary studies, at present, we still lack a general
understanding of the precision with which \(\lambda\) can estimate
levels of phylogenetic signal in phenotypic datasets. \hfill\break

In this study, we evaluate the precision of Pagel's \(\lambda\) to
estimate known levels of phylogenetic signal in phenotypic data. First
we use computer simulations across differing numbers of species, and
differing input levels of phylogenetic signal to explore when
\(\lambda\) captures known levels of phylogenetic signal, and under what
circumstances. Additionally, we use simulations to determine how the
inclusion of \(\lambda\) in phylogenetic ANOVA and regression (i.e.,
PGLS) affects parameter estimation, and whether estimates of
phylogenetic signal in PGLS are accurate. We then survey the recent
macroevolutionary literature for published papers containing estimates
of \(\lambda\) from empirical datasets, and compare these empirical
estimates to patterns gleaned from our computer simulations. In general
we find that while PGLS parameters are accurately estimated with the
inclusion of phylogenetic signal, estimates of \(\lambda\) are not.
Thus, empirical studies should interpret the degree of phylogenetic
signal in phenotypic data with caution when using this parameter.
\textbf{something more? Let's wait for final data to decide.}

\hypertarget{methods-and-results}{%
\section{Methods and Results}\label{methods-and-results}}

\hypertarget{simulated-trait}{%
\subsection{\texorpdfstring{\emph{Simulated
trait}}{Simulated trait}}\label{simulated-trait}}

@@

\hypertarget{simulated-anova-and-regressions}{%
\subsection{\texorpdfstring{\emph{Simulated ANOVA and
Regressions}}{Simulated ANOVA and Regressions}}\label{simulated-anova-and-regressions}}

@@

Scaling and trait generation procedures for all simulation methods were
repeated with symmetrical and ladder phylogenies of variable size.
Results generated using these variable phylogeny shapes were consistent
with the pure-birth phylogeny results presented above and can be found
in the Supplemental Materials. All analyses were performed in R v3.6.0
(R Core Team 2019) using the packages \texttt{geiger} (Harmon et al.
2008) and \texttt{caper} (Orme et al. 2013), and the corresponding
scripts can be found in the Supplemental Materials.

\hypertarget{meta-analysis-of-empirical-results}{%
\subsection{\texorpdfstring{\emph{Meta-Analysis of Empirical
Results}}{Meta-Analysis of Empirical Results}}\label{meta-analysis-of-empirical-results}}

To understand the extent of this problematic estimation method in
application, we performed a meta-analysis of studies published in 2019
that cited Pagel's 1997 manuscript (Pagel 1999). The list of manuscripts
was compiled through Google Scholar on Jan 23, 2020 and totaled 341
manuscripts. For each study, we extracted any published lambda
estimates, along with the size of the phylogeny used in the analysis. We
also noted whether authors reported confidence intervals, significance
tests assessing difference of the lambda estimate from 0 or 1, and
whether authors interpreted biological meaning from the magnitude of the
estimated lambda. For studies that reported more than one lambda
estimate, we also noted if the authors compared the lambdas against one
another, and whether that was accompanied with an appropriate
statistical test between the estimated lambda values. \hfill\break

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Abouheif1999}{}%
Abouheif, E. 1999. A method for testing the assumption of phylogenetic
independence in comparative data. Evolutionary Ecology Research
1:895--909.

\leavevmode\hypertarget{ref-Adams2014a}{}%
Adams, D. C. 2014a. A generalized Kappa statistic for estimating
phylogenetic signal from shape and other high-dimensional dultivariate
data. Systematic Biology 63:685--697.

\leavevmode\hypertarget{ref-Adams2014b}{}%
Adams, D. C. 2014b. A method for assessing phylogenetic least squares
models for shape and other high-dimensional multivariate data. Evolution
68:2675--2688.

\leavevmode\hypertarget{ref-AdamsCollyer2018b}{}%
Adams, D. C., and M. L. Collyer. 2018. Phylogenetic anova: Group-clade
aggregation, biological challenges, and a refined permutation procedure.
Evolution 72:1204--1215.

\leavevmode\hypertarget{ref-Beaulieu_et_al2012}{}%
Beaulieu, J. M., D. C. Jhwueng, C. Boettiger, and B. C. O'Meara. 2012.
Modeling stabilizing selection: Expanding the ornstein-uhlenbeck model
of adaptive evolution. Evolution 66:2369--2383.

\leavevmode\hypertarget{ref-Blomberg_et_al2003}{}%
Blomberg, S. P., T. Garland, and A. R. Ives. 2003. Testing for
phylogenetic signal in comparative data: Behavioral traits are more
labile. Evolution 57:717--745.

\leavevmode\hypertarget{ref-Boettiger_et_al2012}{}%
Boettiger, C., G. Coop, and P. Ralph. 2012. Is your phylogeny
informative? Measuring the power of comparative methods. Evolution
67:2240--2251.

\leavevmode\hypertarget{ref-ButlerKing2004}{}%
Butler, M. A., and A. A. King. 2004. Phylogenetic comparative analysis:
A modeling approach for adaptive evolution. American Naturalist
164:683--695.

\leavevmode\hypertarget{ref-DinizFilho2012}{}%
Diniz-Filho, J. A. F., T. Santos, T. F. Rangel, and L. M. Bini. 2012. A
comparison of metrics for estimating phylogenetic signal under
alternative evolutionary models. Genetics and molecular biology
35:673--679. SciELO Brasil.

\leavevmode\hypertarget{ref-Felsenstein1985}{}%
Felsenstein, J. 1985. Phylogenies and the comparative method. American
Naturalist 125:1--15.

\leavevmode\hypertarget{ref-Freckleton_et_al2002}{}%
Freckleton, R. P., P. H. Harvey, and M. Pagel. 2002. Phylogenetic
analysis and comparative data: A test and review of evidence. American
Naturalist 160:712--726.

\leavevmode\hypertarget{ref-GarlandIves2000}{}%
Garland, T. J., and A. R. Ives. 2000. Using the past to predict the
present: Confidence intervals for regression equations in phylogenetic
comparative methods. American Naturalist 155:346--364.

\leavevmode\hypertarget{ref-Gittleman1990}{}%
Gittleman, J. L., and M. Kot. 1990. Adaptation: Statistics and a null
model for estimating phylogenetic effects. Systematic Zoology
39:227--241. Society of Systematic Zoology.

\leavevmode\hypertarget{ref-Grafen1989}{}%
Grafen, A. 1989. The phylogenetic regression. Philosophical Transactions
of the Royal Society of London B, Biological Sciences 326:119--157.

\leavevmode\hypertarget{ref-Harmon2008}{}%
Harmon, L. J., J. T. Weir, C. D. Brock, R. E. Glor, and W. Challenger.
2008. GEIGER: Investigating evolutionary radiations. Bioinformatics
24:129--131.

\leavevmode\hypertarget{ref-HarveyPagel1991}{}%
Harvey, P. H., and M. D. Pagel. 1991. The comparative method in
evolutionary biology. Oxford University Press, Oxford.

\leavevmode\hypertarget{ref-Klingenberg2010}{}%
Klingenberg, C. P., and N. A. Gidaszewski. 2010. Testing and quantifying
phylogenetic signals and homoplasy in morphometric data. Systematic
biology 59:245--261. Oxford University Press.

\leavevmode\hypertarget{ref-MartinsHansen1997}{}%
Martins, E. P., and T. F. Hansen. 1997. Phylogenies and the comparative
method: A general approach to incorporating phylogenetic information
into the analysis of interspecific data. American Naturalist
149:646--667.

\leavevmode\hypertarget{ref-MolinaVenegas2017}{}%
Molina-Venegas, R., and M. A. Rodriguez. 2017. Revisiting phylogenetic
signal; strong or negligible impacts of polytomies and branch length
information? BMC evolutionary biology 17:53. BioMed Central.

\leavevmode\hypertarget{ref-Munkemuller_et_al2012}{}%
Munkemuller, T., S. Lavergne, B. Bzeznik, S. Dray, T. Jombart, K.
Schiffers, and W. Thuiller. 2012. How to measure and test phylogenetic
signal. Methods in Ecology and Evolution 3:743--756.

\leavevmode\hypertarget{ref-OMeara_et_al2006}{}%
O'Meara, B. C., C. Ane, M. J. Sanderson, and P. C. Wainwright. 2006.
Testing for different rates of continuous trait evolution using
likelihood. Evolution 60:922--933.

\leavevmode\hypertarget{ref-Orme2013}{}%
Orme, D., R. P. Freckleton, G. H. Thomas, T. Petzoldt, S. A. Fritz, and
N. Isaac. 2013. CAPER: Comparative analyses of phylogenetics and
evolution in r. Methods in Ecology and Evolution 3:145--151.

\leavevmode\hypertarget{ref-Pagel1999}{}%
Pagel, M. D. 1999. Inferring the historical patterns of biological
evolution. Nature 401:877--884.

\leavevmode\hypertarget{ref-Pavoine2012}{}%
Pavoine, S., and C. Ricotta. 2012. Testing for phylogenetic signal in
biological traits: The ubiquity of cross-product statistics. Evolution:
International Journal of Organic Evolution 67:828--840. Wiley Online
Library.

\leavevmode\hypertarget{ref-RCT}{}%
R Core Team. 2019. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\leavevmode\hypertarget{ref-Revell2010}{}%
Revell, L. J. 2010. Phylogenetic signal and linear regression on species
data. Methods in Ecology and Evolution 1:319--329.

\leavevmode\hypertarget{ref-RevellHarmon2008}{}%
Revell, L. J., and L. J. Harmon. 2008. Testing quantitative genetic
hypotheses about the evolutionary rate matrix for continuous characters.
Evolutionary Ecology Research 10:311--331.

\leavevmode\hypertarget{ref-Revell_et_al2008}{}%
Revell, L. J., L. J. Harmon, and D. C. Collar. 2008. Phylogenetic
signal, evolutionary process, and rate. Systematic Biology 57:591--601.

\leavevmode\hypertarget{ref-Rohlf2001}{}%
Rohlf, F. J. 2001. Comparative methods for the analysis of continuous
variables: Geometric interpretations. Evolution 55:2143--2160.

@@

\hypertarget{figure-legends}{%
\section{Figure Legends}\label{figure-legends}}
